### 2016-08-25 analysis-note-v2/Appendix.tex
fix a reference in figure G.1
fixed the reference in Appendix G and clean more the text

\chapter{Free proton beam-spin asymmetry interpolation} 
\label{app:free-proton-alu}
\section{Fitting the experimentally measured asymmetries}
Following the discussion in section \ref{sec:Generalized_EMC}, comparing the 
coherent and the incoherent beam-spin asymmetries to free proton asymmetries 
reveal new information about the nuclear medium modifications. To construct 
such ration, the published free proton asymmetries \cite{FX_BSA} have been used 
in this analysis, see figure \ref{fig:free-proton-alu}. The measured free 
proton $A_{LU}$ at $\phi = 90^{\circ}$ were fitted as a function of $-t$ in the 
different bins in $x_B$ and $Q^2$. Then, the parameters of the fits were 
parametrized as a function of $x_B$ assuming that the dependence on $Q^2$ is 
negligible, figure \ref{fig:free-proton-alu}. Finally, the free proton 
asymmetries were calculated at the same incoherent and coherent measured 
kinematics. The statistical errors on the calculated asymmetries were 
calculated using the error bars on the fitted parameters $t_{min}$, $p_0$, and 
$p_1$.\\

@@

\begin{figure}[tpb]
   \centering
\includegraphics[scale=0.37]{fig_updated/tmin-xB-fit.png}\\
\includegraphics[scale=0.37]{fig_updated/p0-xB-fit.png}\\
\includegraphics[scale=0.37]{fig_updated/p1-xB-fit.png}
\caption{The fitted $t_{min}$, $p_0$, and $p_1$ parameters as a function of 
$x_B$.}
\label{fig:free-proton-alu}
\end{figure}

\section{Model-dependent extraction}
The proton asymmetries have been adjusted using a dispersion calculation 
including a phenomenological GPD $H$ only. The imaginary part of the amplitude 
is parameterized as in \cite{GPD_cal_free_p}. The real part of the amplitude is 
then obtained from the dispersion relation and the D-term as subtraction 
constant, parameterized as in \cite{GPD_cal_free_p}. The beam spin asymmetries 
mostly constrain the parameters of the imaginary part, and the unpolarized 
cross-section mostly constrain the D-term parameters.

\begin{figure}[tpb]
   \centering
\includegraphics[scale=0.55]{fig_updated/From_FX_Check_Fit_6GeV_asym.png}
\caption{The free proton beam-spin asymmetries at $\phi = 90^{circ}$ as a 
function of $-t$ in different ($x_B, Q^2$) bins as measured at CLAS-E1DVCS 
experiment. The solid red lines are the model calculations based on the 
kinematics of each bin. The blue points stand for the interpolated free proton 
asymmetries at the kinematics of our incoherent and coherent DVCS channels.}
\label{fig:free-proton-alu}
\end{figure}

\section{Summary}
In this analysis we use the interpolated values from fitting the experimentally 
measured free proton asymmetries to construct the beam-spin asymmetry ratios.  
The differences between the beam-spin asymmetry ratios calculated using the 
fitting the free proton asymmetries and the model-dependent interpolated values 
were added as a systematic errors on the constructed beam-spin asymmetry 
ratios. Table \ref{table:ALU_ratios_} presents the coherent and the incoherent 
$A_{LU}$ ratios extracted using both methods and the associated systematic 
uncertainties.

>>>>

\chapter{Free proton beam-spin asymmetry interpolation} 
\label{app:free-proton-alu}
\section{Fitting the experimentally measured asymmetries} \label{fit_int} 
Following the discussion in section \ref{sec:Generalized_EMC}, comparing the 
coherent and the incoherent beam-spin asymmetries to free proton asymmetries 
reveal new information about the nuclear medium modifications. To construct 
such ratio, the published free proton asymmetries \cite{FX_BSA} have been used 
in this analysis, see figure \ref{fig:free-proton-alu}. The measured free 
proton $A_{LU}$ at $\phi = 90^{\circ}$ were fitted as a function of $-t$ for 
the different bins in $x_B$ and $Q^2$. Then, the parameters of the fits were 
parametrized as a function of $x_B$ assuming that the dependence on $Q^2$ is 
negligible, figure \ref{fig:free-proton-alu}. Finally, the free proton 
asymmetries were calculated at the same incoherent and coherent measured 
kinematical values. The statistical errors on the calculated asymmetries were 
calculated using the error bars on the fitted parameters $t_{min}$, $p_0$, and 
$p_1$.\\

@@

\begin{figure}[tpb]
   \centering
\includegraphics[scale=0.37]{fig_updated/tmin-xB-fit.png}\\
\includegraphics[scale=0.37]{fig_updated/p0-xB-fit.png}\\
\includegraphics[scale=0.37]{fig_updated/p1-xB-fit.png}
\caption{The fitted $t_{min}$, $p_0$, and $p_1$ parameters as a function of 
$x_B$.}
\label{fig:fitted-points-xB}
\end{figure}

\section{Model-dependent extraction} \label{model_int}
The proton asymmetries have been adjusted using a dispersion calculation 
including a phenomenological GPD $H$ only. The imaginary part of the amplitude 
is parameterized as in \cite{GPD_cal_free_p}. The real part of the amplitude is 
then obtained from the dispersion relation and the D-term as subtraction 
constant, parameterized as in \cite{GPD_cal_free_p}. The beam spin asymmetries 
mostly constrain the parameters of the imaginary part, and the unpolarized 
cross-section mostly constrain the D-term parameters. Figure 
\ref{fig:FXfree-proton-alu} presents the published free proton asymmetries with 
the model calculations, in solid red lines, and the interpolated free proton 
asymmetries at our incoherent and coherent measured kinematical values.

\begin{figure}[tpb]
   \centering
\includegraphics[scale=0.55]{fig_updated/From_FX_Check_Fit_6GeV_asym.png}
\caption{The free proton beam-spin asymmetries at $\phi = 90^{circ}$ as a 
function of $-t$ in different ($x_B, Q^2$) bins as measured at CLAS-E1DVCS 
experiment. The solid red lines are the model calculations based on the 
kinematics of each bin. The blue points stand for the interpolated free proton 
asymmetries at the kinematics of our incoherent and coherent DVCS channels.}
\label{fig:FXfree-proton-alu}
\end{figure}

\section{Summary}
In this analysis we use the interpolated values from fitting the experimentally 
measured free proton asymmetries to construct the beam-spin asymmetry ratios, 
presnted in section \ref{fit_int}.  The differences between the beam-spin 
asymmetry ratios calculated using the free proton asymmetries fits, section 
\ref{fit_int}, and the model-dependent interpolated values, section 
\ref{model_int}, were added as a systematic errors on the constructed beam-spin 
asymmetry ratios.  Table \ref{table:ALU_ratios_} presents the coherent and the 
incoherent $A_{LU}$ ratios extracted using both methods and the associated 
systematic uncertainties.
